---
title: Synthetic Data
output:
  html_document: 
    df_print: paged
---

# Synthetic Data

Our goal is to create a set of customer data that looks "real" - either record by record, or as a whole dataset.

## Record Level Synthetic Data

### charlatan

`charlatan` is a package that feels a bit incomplete, but very easily generates a lot of useful sequences of data, from names and phones numbers, latitudes and longitudes, to genetic sequences and scientific names.

For example, here's synthetic data generated for 10 customers, with:

 - Names that might not be clean (e.g. may have titles or qualifications)
 - One job that is written in French
 - Phone numbers in multiple locales, with missingness
 - Credit card numbers

```{r charlatan}
library(charlatan)

set.seed(1)

customers <- data.frame(
  Name = ch_name(10, messy=TRUE),
  Job = c(ch_job(9), ch_job(locale="fr_FR")),
  Contact = MissingDataProvider$new()$make_missing(ch_phone_number(10)),
  CreditCard = ch_credit_card_number(10)
)

customers

```

## Dataset Level Synthetic Data

### fabricatr

`fabricatr` enables simple relationships between variables to be specified, but needs some effort put in.

For each of the 10 customers above we'll generate 10 transactions:

 - Uniformly distributed throughout the year
 - Where each customer generally increases their payments through the year,
 - Where each customer has a general level of payment, and
 - The minimum payment is approximately 5

```{r fabricatr}
library(fabricatr)

set.seed(1)

customer_transactions <- fabricate(
  N = 100,
  Name = rep(customers$Name, 10),
  DayOfYear = draw_categorical(prob=matrix(1/365, 100, 365)),
  Payment = round(
    draw_normal_icc(
      mean = 5, 
      sd = 1, 
      N = N, 
      clusters = Name, 
      ICC = 0.9)
    * DayOfYear/20 + 
    pmax(
      draw_normal_icc(
        mean = 20, 
        sd = 20, 
        N = N, 
        clusters = Name, 
        ICC = 0.6), 
      5 + rgamma(100, 1)
      ), 
    2)
)

customer_transactions[order(customer_transactions$Payment),]
```

```{r, echo=FALSE}
library(ggplot2)
library(gridExtra)

g1 <- ggplot(data = customer_transactions, aes(x = DayOfYear, y = Payment, colour = Name)) + geom_point() + geom_line()

g1
```

## synthpop

`synthpop` also generates synthetic datasets, but in a very straightforward way - taking a sample dataset and producing a dataset that looks pretty similar to the sample data.

Below we try this on the transactions dataset that was generated above.

```{r synthpop}
library(synthpop)

customer_transactions2 <- syn(customer_transactions[,-1], seed = 1)$syn

customer_transactions2[order(customer_transactions2$Payment),]
```
```{r, echo=FALSE, out.width = "150%"}
g2 <- ggplot(data = customer_transactions2, aes(x = DayOfYear, y = Payment, colour = Name)) + geom_point() + geom_line() + theme(legend.position = 'none')

grid.arrange(g1 + theme(legend.position = 'none'), g2, ncol=2)
```
